Jug: Software for Reproducible Computation

### 2012-01-24 paper.tex
TXT Comments on splitting computation/figures
Often, the problem of "this computation takes a few computer years" is
not properly acknowledged.

\section{Discussion}
Unlike most previous tools for reproducible research, jug focuses on the
development of the computation as much as its communication (in fact, when it
comes to communication other tools might be better suited as they combine
written exposition with computer code). While it still possible to make errors
(for example, by changing the code but neglecting to invalidate the results),
jug improves the pipeline development experience and makes the programming
researcher more productive.

Jug was not designed to compete with more complex map/reduce frameworks such as
Hadoop, which scale better to very large projects. However, those frameworks
have much higher costs in terms of development time (code must be written
especially for the framework) and overhead (starting up and shutting down jobs
can take much longer and using non-Java code has additional computational
costs). For scientists using small to medium-sized cluster (hundreds, not
thousands, of nodes), with a shared file-system (as opposed to the distributed
file-systems necessary for truly large amounts of data) jug might provide a
better trade-off  than those higher-powered alternatives.

>>>>

\section{Discussion}
Unlike most previous tools for reproducible research, jug focuses on the
development of the computation as much as its communication. In fact, when it
comes to communication other tools might be better suited as they combine
written exposition with computer code. They can be used in combination with jug
as they do not often provide caching and distribution, needed for large
projects. While the simplest mode of jug use is to have a single
\textit{jugfile}, a jugfile can import the results of another. For example, a
first jugfile might perform all heavy-duty computation and be run on a
computing cluster. A second script could be embedded inside an executable paper
to generate tables and plots \citep{Delescluse2011}. This faster script could
be run as part of building the paper (while the longer script would take too
long).

While it still possible to make errors (for example, by changing the code but
neglecting to invalidate the results), jug improves the pipeline development
experience and makes the programming researcher more productive and less
error-prone.

Jug was not designed to compete with complete map/reduce frameworks such as
Hadoop, which scale better to very large projects. However, those frameworks
have much higher costs in terms of development time (code must be written
especially for the framework) and overhead (starting up and shutting down jobs
can take much longer and using non-Java code has additional computational
costs). For scientists using small to medium-sized cluster (hundreds, not
thousands, of nodes), with a shared file-system (as opposed to the distributed
file-systems necessary for truly large amounts of data) jug might provide a
better trade-off than those higher-powered alternatives.
